---
title: "Extra Credit Assingment"
author: "Harrison Popp"
date: "4/22/2020"
output: html_document
---

```{r}
library(readr)
AXISBANK <- read_csv("Nifty50/AXISBANK.csv")
library(tidyverse)
library(tidymodels)
library(ISLR)
install.packages("ranger")
```

The research question I am looking to answer here is what relationships do the low, previous close, open, and volume for the stock UTIBANK ticker affect the prediction for the high that day? I want to use these variables to predict the high of the stock price for each day


```{r, Tuning to get penalty}
ridge_spec <- linear_reg(penalty = tune(), mixture = 0) %>%
  set_engine("glmnet")

grid <- expand_grid(penalty = seq(0, 10, by = 1))

rec <- recipe(Close ~ Volume + Open + High + Low, data = AXISBANK) %>%
  step_scale(all_predictors()) %>%
  step_dummy(all_nominal())

results <- tune_grid(ridge_spec,
                     preprocessor = rec,
                     grid = grid,
                     resamples = Axis_cv)
results%>%
  collect_metrics()%>%
  filter(.metric == "rmse")%>%
  arrange(mean)
```

I decidided to tune the penalty for the model, I first tuned from 0-100 by 10s then realizes 0 was the best, and then did 0-10 by 1s and found 0 to still be the best, so I used that in my model.

```{r}
ridge_final <- linear_reg(penalty = 0, mixture = 0) %>%
  set_engine("glmnet")
rec2 <- recipe(Close ~ Volume + Open + High + Low, data = AXISBANK) %>%
  step_scale(all_predictors()) %>%
  step_dummy(all_nominal())

rec2
```

For my evaluation, I think that this model is not the best option for this data set, it is not easy to understand and I was not able to gain any insight into where the stock will close the day on price. I think that tuning worked well except that tuning led to 0 which is essentially linear regression so ridge may not have been a great choice. I think if I could have chosen from models outside of what we have worked on in class I would have used some QDA then linear regression and depending on the fit transform the data if needed. I do think this was an interesting experience where I learned a lot more about R and had to research on my own. I did enjoy looking through data sets trying to find interesting sets that I would want to try and predict some relationship. At first I wanted to use a National Hockey League dataset but it was pretty dated and didn't have the variables I was hoping for so I transitioned into any stock market information I could find and that's how I ended up with this.
